### 2016-01-06 p2/intro.tex
New reference

A central problem of command-based synchronizers 
during both update detection and reconciliation
is the ordering (scheduling) of commands.
If update detection is based on comparing the original state of the filesystem
to its new state, then we can easily collect a set of updates,
but we need to order these in a way that they could be applied
to the filesystems without causing an error 
(for example, a directory needs to be created before a file can be created under it).
Similarly, during reconciliation when we consider all the updates that
have been applied to the different replicas, we need to find a way of
merging these and creating a global ordering that we can apply
to the filesystems.
In fact, an insight in \cite{NREC} is that
if the ordering changes the effect of two commands (updates),
then under certain circumstances they are not compatible and will give rise to conflicts.
Accordingly, in this paper command-pairs and their properties
play a special role.
Other research also shows the essential nature of ordering:
in IceCube multiple orders are tested to find an acceptable one \cite{KRSD},
or in Bayou reconciling updates happens by redoing them in an acceptable order \cite{TTPDSH}.
Saito and Shapiro offer a survey of so-called optimistic replication algorithms in which
ordering (scheduling) plays a central role (\cite{SSH}).

>>>>

A central problem of command-based synchronizers 
during both update detection and reconciliation
is the ordering (scheduling) of commands.
If update detection is based on comparing the original state of the filesystem
to its new state, then we can easily collect a set of updates,
but we need to order these in a way that they could be applied
to the filesystems without causing an error 
(for example, a directory needs to be created before a file can be created under it).
Similarly, during reconciliation when we consider all the updates that
have been applied to the different replicas, we need to find a way of
merging these and creating a global ordering that we can apply
to the filesystems.
In fact, an insight in \cite{NREC} is that
if the ordering changes the effect of two commands (updates),
then under certain circumstances they are not compatible and will give rise to conflicts.
Accordingly, in this paper command-pairs and their properties
play a special role
as we aim to find valid orderings on filesystem trees
(also known as semantic scheduling)
as opposed to syntactic scheduling that follows the strict temporal order
of updates and may give rise to otherwise resolvable conflicts (\cite{SSH}).
Other research also shows the essential nature of ordering:
Saito and Shapiro offer a survey of so-called optimistic replication algorithms in which
it plays a central role (\cite{SSH});
in IceCube multiple orders are tested to find an acceptable one (\cite{KRSD}, see also \cite{MPV}),
or in Bayou reconciling updates happens by redoing them in an acceptable order \cite{TTPDSH}.
